Allocation Removal by Partial Evaluation in a Tracing JIT

### 2011-01-11 talk/pepm2011/presentation/talk.tex
backup slides

>>>>

\begin{frame}
  \frametitle{Backup Slides}
\end{frame}

\begin{frame}
  \frametitle{What About Correctness?}
  \begin{itemize}
      \item We haven't proven correctness yet
      \item should not be too hard
      \item lifting needs to be carefully handled
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Comparison to Escape Analysis}
  \begin{itemize}
      \item Effect very similar to escape analysis
      \item Escape analysis needs a complex upfront analysis
      \item our optimization automatically has a lot of context, due to the inlining tracing does
      \item our optimization can optimize operations on objects even if they escape later
  \end{itemize}
\end{frame}

\begin{frame}[containsverbatim]
  \frametitle{Comparison to "Dynamic Typing"/Boxing Analysis}
  \begin{itemize}
      \item those optimizations work ahead of time
      \item don't work for many dynamic languages, where the source simply does not contain enough information
  \end{itemize}

  \begin{block}{Python Example:}
  \begin{verbatim}
def sum(container, initial):
    result = initial
    for element in container:
        result = result + element
    return result
  \end{verbatim}
  \end{block}
\end{frame}
